RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-07-04 background.tex
added a new small example
fixed the error

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/example_small}
\caption{Partial GRL Model of Traffic Simulator Example %(\todo{Marc}{Sepideh}{Turn into vector image, turn ``Dynamic simulation'' and ``Static Simulation'' into goals, turn ``Simulate'' into softgoal, add some resource}}
\label{fig:example-small}
\end{figure} %SG: I changed the figure a bit so that we won't need to change Figure 10. Let me know if you still want to change them according to the above.

@@

These are the type of the questions that we cannot answer by just looking at GRL models. The model in Figure~\ref{fig:example-small} does not contain information about discussions that lead to the resulting model, such as various clarification steps for the naming, or alternatives that have been considered for the relationships. In this article we aim to address this shortcoming.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/Example1}
\caption{Partial GRL Model of Traffic Simulator Example} %(\todo{Marc}{Sepideh}{Turn into vector image, turn ``Dynamic simulation'' and ``Static Simulation'' into goals, turn ``Simulate'' into softgoal, add some resource}}
\label{fig:example-small}
\end{figure} %SG: I changed the figure a bit so that we won't need to change Figure 10. Let me know if you still want to change them according to the above.

@@

These are the type of the questions that we cannot answer by just looking at GRL models. The model in Figure~\ref{fig:Example1} does not contain information about discussions that lead to the resulting model, such as various clarification steps for the naming, or alternatives that have been considered for the relationships. In this article we aim to address this shortcoming.
